# Figures & Plots

## Basics
### Building a plot using ggplot2

#### Packages and Sample Data
```{r, echo = TRUE, message = FALSE, warning = FALSE}
# Packages
library(haven)
library(ggplot2)

# Data
adam_path <- "https://github.com/phuse-org/TestDataFactory/raw/main/Updated/TDF_ADaM/"
adsl <- as.data.frame(haven::read_xpt(paste0(adam_path, "adsl.xpt")))
```

Let's create a basic scatter plot of weight vs height.
```{r, eval = F}
# basic scatter plot of weight vs height
my_scatter_plot <- ggplot(adsl, aes(x = HEIGHTBL, y = WEIGHTBL)) +
  geom_point()
my_scatter_plot
```


### Exporting plots
You may export plots as png files a few ways. If your plot is created in ggplot2, you can use the `ggsave()` function to export as png:
```{r, eval = F}
# save plot as a png file
ggsave(plot = my_scatter_plot, 
       filename = "my_plot_output_1.png", 
       width = 7, 
       height = 5, 
       units = "in")
```

The more general way to save plots as png files is to use the `png()` function. It can work with ggplot2, but also plots created in base R.
```{r, eval = F}
png(filename = "my_plot_output_2.png", 
    width = 7, 
    height = 5, 
    units = "in", 
    res = 300)

print(my_scatter_plot)
dev.off()
```

## Examples

### Swimmer Plot

For this example we use the **swimplot** package for plotting. It makes the creation of swimmer plots very easy and is based on ggplot2 and thus allows nice customizations. However, if even more customization is required, swimmer plots can also be created by using ggplot2 only.  

A little demo how you could use the package is given below, in case you would like to find out more, you can check out [this](https://cran.r-project.org/web/packages/swimplot/vignettes/Introduction.to.swimplot.html). 


#### Packages and Sample Data
```{r, message = F, warning = F}
# Packages
library(haven)
library(swimplot)
library(dplyr)

# Data
adam_path <- "https://github.com/phuse-org/TestDataFactory/raw/main/Updated/TDF_ADaM/"
adsl <- haven::read_xpt(paste0(adam_path, "adsl.xpt"))
adae <- haven::read_xpt(paste0(adam_path, "adae.xpt"))
adtte <- haven::read_xpt(paste0(adam_path, "adtte.xpt"))
```

We have to apply some changes to the data so that they can be processed by the plot functions later on. The number of subjects is limited to 50 for display purposes and we create our own response duration variable because we only have the start date of the event given in those data.

```{r, message = F}
adsl_new <- adsl %>%
  select(USUBJID, ARM, TRTDURD, SEX) %>%
  slice(1:50) 
adae_new <- adae %>%
  select(USUBJID, AEDECOD, AESEV, AEREL, ASTDY) %>%
  filter(USUBJID %in% adsl_new$USUBJID & ASTDY >= 0)
adtte_new <- adtte %>%
  select(USUBJID, EVNTDESC, AVAL) %>%
  filter(USUBJID %in% adsl_new$USUBJID & EVNTDESC != "Study Completion Date")  
random_duration_of_events <- sample(1:25, nrow(adtte_new), replace = T)
adtte_new <- adtte_new %>% 
  bind_cols(random_duration_of_events) %>%
    mutate(Resp_end = AVAL + random_duration_of_events )
adsl_new <- as.data.frame(adsl_new)
adae_new <- as.data.frame(adae_new)
adtte_new <- as.data.frame(adtte_new)
```

#### Basic swimmer plot

A basic swimmer plot just consists of a simple bar chart. 
```{r}
swimmer_plot(df=adsl_new,
             id='USUBJID',
             end='TRTDURD',
             fill='lightblue',
             width=.85)
```

Now, treatment information is added. 

```{r}
arm_plot <- swimmer_plot(df=adsl_new,
                         id='USUBJID',
                         end='TRTDURD',
                         name_fill='ARM',
                         id_order='ARM',
                         col="black",
                         alpha=0.75,
                         width=.8)
arm_plot
```


The plot could be stratified by any other variable of interest, in this case: SEX. 
```{r}
swim_plot_stratify <-swimmer_plot(df=adsl_new,
                                  id='USUBJID',
                                  end='TRTDURD',
                                  name_fill='ARM',
                                  col="black",
                                  alpha=0.75,
                                  width=.8,
                                  base_size=14,
                                  stratify= c('SEX'))
swim_plot_stratify
```


#### Adding adverse event information to the plot

```{r}
AE_plot <- arm_plot + 
  swimmer_points(df_points=adae_new,
                 id='USUBJID',
                 time='ASTDY',
                 name_shape='AESEV',
                 size=2.5,
                 fill='white', 
                 name_col='AEREL')
AE_plot
```

#### Adding time-to-event information to the plot

```{r, message = F, warning = F}
Response_plot <- arm_plot +
  swimmer_lines(df_lines=adtte_new,
                id='USUBJID',
                start ='AVAL',
                end='Resp_end',
                name_col='EVNTDESC',
                size=1)
Response_plot
```

#### Customize plot

```{r, message = F, warning = F}
Response_plot_with_points <- Response_plot +
  swimmer_points_from_lines(df_lines=adtte_new,
                            id='USUBJID',
                            start='AVAL',
                            end='Resp_end',
                            name_col='EVNTDESC',
                            size=2) +
  scale_fill_manual(name="Treatment",
                    values=c("Placebo" ="#A9342F", 
                             "Xanomeline High Dose"="#5B7ACE",
                             "Xanomeline Low Dose"='#FFC300'))+
  scale_color_manual(name="Response",
                     values=c("grey20"))+
  scale_shape_manual(name='',
                     values=c(17,15),
                     breaks=c('AVAL','Resp_end'),
                     labels=c('Response start','Response end'))+
  guides(fill = guide_legend(override.aes = list(shape = NA))) +
  scale_y_continuous(name = "Time since enrollment")

Response_plot_with_points
```

### Waterfall Plot
#### Packages and Sample Data

```{r, message = FALSE, warning = FALSE, error = FALSE}
# Packages
library(gridExtra)
library(grid)

# Data
wp <- data.frame(subjidn = 1:30,
                 trtp = sample(c('Drug','Placebo'), replace = T, 30),
                 aval = runif(30, min = -40, max = 40))
```

```{r echo = F}
head(wp) %>% 
  kableExtra::kable(align = 'c')
```

#### Basic Waterfall Plot
Create an initial waterfall plot

```{r, message = FALSE, warning = FALSE, error = FALSE}
basic_waterfall <- ggplot(wp, aes(y = aval,x = reorder(subjidn, -aval))) +
  geom_bar(stat = "identity")

basic_waterfall
```


#### Adding Customizations
Add a few customizations to the waterfall plot

1. Bar fill color is determined by trtp value
2. Specify custom colors, name the legend
3. Specify Y-axis goes from -40 to 40, by increments of 10
4. Add in a Y-axis label
5. Specify a base theme
6. Remove the X-axis
7. Move legend to bottom of graph

#### Customized Waterfall Plot

```{r, message = FALSE, warning = FALSE, error = FALSE}
custom_waterfall <- ggplot(wp, aes(y = aval, x = reorder(subjidn, -aval), fill = trtp)) +                            
  geom_bar(stat = "identity") +
  scale_fill_manual("Planned Treatment Arm", values = c('#00bbff','#89d329')) +
  scale_y_continuous(limits = c(-40,40), breaks = seq(-40, 40, by = 10)) +      
  ylab("Maximum reduction of tumor size (%)\n") +                              
  theme_light() +                                                               
  theme(axis.title.x = element_blank(),                                         
        axis.line.x  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "bottom")                                             
          
custom_waterfall
```

#### Study Example

* A special waterfall plot layout is needed in a real study. In this layout, biomarker information in the subject level needs to be added at the bottom of the waterfall plots.

* The dataset for the plot was derived from ADRS and ADSL in SAS; simulated data is used in this demo.

Simulate Data:
```{r,  message=FALSE, warnings=FALSE}
set.seed(100)  

n <- 120   # size/records of simulated data

dat_all <- 
  data.frame(SUBJID = 120010100:(120010100+n-1),
           AVAL = c(rnorm(round(0.8*n), 0, 20), rep(0, round(0.2*n))) %>% sample(),
           OVERALLRESP = c("PR", "SD","PD") %>% sample(size=n, replace=TRUE),
           AMEDGRPN = seq(10, 50, 10) %>% sample(size=n, replace=TRUE),
           DOR = rpois(n, 40),
           AVISIT = c("C1", "C2", "C3","EOT") %>% sample(size=n, replace=TRUE),
           ATMLOSS_L = c("E", "L", "Data unavailable") %>% sample(size=n, replace=TRUE),
           ATMLOSS_P = c("E", "L", "Data unavailable") %>% sample(size=n, replace=TRUE),
           ATMLOSS_R = c("E", "L", "Data unavailable") %>% sample(size=n, replace=TRUE),
           IDFOOT = "Bayer: /study/path/.../f_waterfall.sas               30NOV2021 16:06"
           ) %>%
  mutate_at(vars("OVERALLRESP", "DOR", "IDFOOT"), as.character)
```

* X: SUBJID 
* Y: AVAL (derived from ADRS.AVAL when ADRS.PARAM = "Maximum Tumor Reduction (%)") 
* Label: OVERALLRESP (derived from ADRS.AVAL when ADRS.PARAM = "Best Overall Response") 
* Subset: AMEDGRPN (5 groups)
* A graph function is created in the real study for different analysis groups, in this demo, we subset data to AMEDGRPN = 50. 

```{r, echo=FALSE, message=FALSE, warnings=FALSE}
dat_all %>% 
  filter(AMEDGRPN==50) %>% 
  select(SUBJID, AVAL, OVERALLRESP, AMEDGRPN, 
         DOR, AVISIT, ATMLOSS_L, ATMLOSS_P, ATMLOSS_R) %>%
  head() %>%
  kableExtra::kable(align = 'c')

dat <- dat_all %>% filter(AMEDGRPN==50)
```

**Create a waterfall plot with simulated data and below customization**

1. Add x/y-axis labels through function "labs"
2. SUBJID has long digits, below functions are used to avoid overlapping at x-axis:
    + function stringr::str_wrap: add split character “\n" between digits
    + function gsub: add space between digits to enable the use of str_wrap
    + function stringr::str_replace_all: remove space
3. Specify legend title, order/colors (similar to SAS sgplot - dattrmap)
4. Annotation on the top of the bar when Y=0  
5. Adjust background, legend, and size/color/font of x/y-axis aesthetics through Theme

```{r, message=FALSE, warnings=FALSE, fig.dim = c(9, 4)}
waterfall.plot <- dat %>% ggplot(aes(reorder(SUBJID, -AVAL), AVAL, fill =OVERALLRESP)) + 
    geom_bar(stat="identity") +
  labs(x = "Subject", 
       y = "Best % Change from baseline \n in sum of diameters \n (target lesions)\n") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(gsub("([0-9])([0-9])", "\\1 \\2 ", x), 
                                                     width = 5) %>% 
                     stringr::str_replace_all(" ", "")) +
  scale_fill_manual("Best Response",
                    breaks = c("PR", "SD","PD"),
                    values=c("PR"='#89d329',
                             "SD"="#756bb1",
                             "PD"='#00bbff')) + 
  geom_text(aes(label = if_else(AVAL == 0,OVERALLRESP,""),fontface="bold"), 
            vjust = -1,
            size=3,
            color="black") + theme_bw() +     
  theme(
    axis.text = element_text(size=12,color="black",face = "bold"),  
    axis.title.y = element_text(size=12, face="bold"), 
    axis.title.x = element_blank(),  
    legend.background = element_rect(color = "steelblue", linetype = "solid"),
    legend.justification = c(1, 1), 
    legend.position = c(1, 1),
    legend.direction = "horizontal",
    legend.text = element_text(size=8, color = "black", face = "bold"),
    legend.title = element_text(size=8, color = "black", face = "bold"),  
    plot.caption = element_text(hjust = 0, size = 10, color = "blue"), 
    plot.caption.position =  "plot"
  ) 

waterfall.plot
```

As requested from the study, more information at subject level needs to be added in the bottom of the waterfall plots. Thus, two more plots are created (add-in plot1/2) to display the subject level information. 

* Add-in plot 1: visit and duration of response information at subject level
```{r, message=FALSE, warnings=FALSE, fig.dim = c(9, 3)}
var <- c("DOR", "AVISIT")
var_label <- c("Duration (days)", "Timepoint")

add.plot1 <- dat %>%
  reshape2::melt(measure.vars = eval(var), value.name = "label", variable.name = "layer") %>%
  mutate(layer = factor(layer, levels = var, labels = var_label)) %>%
  ggplot(aes(reorder(SUBJID, -AVAL))) +
  geom_text(aes(y = layer, label = label), size = 3, fontface = "bold") +
  labs(y = "", x = NULL) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(
      size = 10,
      colour = "black",
      face = "bold"
    ),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    panel.grid = element_blank(),
    strip.text = element_blank()
  ) +
  coord_fixed(ratio = .8)
add.plot1
```

* Add-in plot 2: biomarker-related information at subject level, footnotes are added in this plot
  + wrap long footnote by adding "\\n\" or using stringr::str_wrap
  + display SAS macro variable "&idfoot."

Footnotes:
```{r}
footnote1 <- 'Footnote1: "\\n\" can be used to split long footnote into next line.'
footnote2 <- "Footnote2: To avoid manually adding split character. The function stringr::str_wrap	can be used here to wrap the long text with a specified width."
footnote <- lapply(c(footnote1,
                     footnote2,
                     "",
                     dat$IDFOOT[1]),
                   function(x) stringr::str_wrap(x, width=120)) %>% # apply str_wrap to individual footnote
  unlist() %>%       # convert list structure to vector
  str_flatten('\n')  # add split character(new line) between footnotes
```

```{r, error = FALSE, message=FALSE, warnings=FALSE, fig.dim = c(9, 3)}
var <- c("ATMLOSS_L", "ATMLOSS_P","ATMLOSS_R")
var_label <- c("Local", "Prospective", "Retrospective")

add.plot2 <- dat %>%  
  reshape2::melt(measure.vars = eval(var), 
                 value.name = "label",
                 variable.name = "layer") %>%
  mutate(label=case_when(
    label == "L" ~ "ATM Loss",
    label == "E" ~ "ATM Expressed",      
    label == "9" ~ "Data unavailable",
    TRUE ~ label
  )) %>% 
  mutate(layer = factor(layer, levels = rev(var), labels = rev(var_label))) %>% 
  ggplot() +
  aes(reorder(SUBJID, -AVAL), layer, color=label,shape=label) +
  geom_point(size=3)+
  scale_shape_manual(breaks = c("ATM Loss","ATM Expressed", "Data unavailable"), 
                     values = c("ATM Loss"=15,"ATM Expressed"=0, 
                                "Data unavailable"=7))+
  scale_color_manual(values = c("ATM Loss"="black", "ATM Expressed"="black", 
                                "Data unavailable"= 'black'))+
  theme_classic()+
  theme(axis.text=element_text(size=10, colour = "black",face = "bold"),
        axis.title=element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=10, color = "black", face = "bold"),
        legend.position = "bottom",
        panel.border = element_blank(),
        panel.grid = element_blank(), 
        strip.text = element_blank(),
        plot.caption = element_text(hjust = 0, size = 10), 
        plot.caption.position =  "plot"
  )+
  coord_fixed(ratio=.9)+ 
  labs(caption = footnote)
add.plot2
```

* The following functions are used to combine three plots aligned with x value.
  + ggplot2::ggplotGrob
  + gridExtra::gtable_rbind
  + grid::grid.draw
  
* Align the three plots with the same x-axis (SUBJID). 
  + waterfall.plot 
  + add.plot1 
  + add.plot2 
  
```{r, message=FALSE, warnings=FALSE, fig.dim = c(10, 7)}
p1 <- waterfall.plot %>% ggplotGrob()
p2 <- add.plot1 %>% ggplotGrob()
p3 <- add.plot2 %>% ggplotGrob()
gtable_rbind(p1, p2, p3,
             size='first') %>% grid.draw()
```

### Spaghetti Plot
#### Packages and Sample Data
```{r message = F, warning = F}
# Packages
library(gg.gap)

# Data
set.seed(100)  

n <- 50   # number of subjects, each subject has 12 data points

spaghetti_sim <- data.frame(SUBJIDN = rep(1:n,each=12),
                            X = rep(1:12,n),
                            Y = c(rgamma((n*12-5), 5, 1), rnorm(5, 200,40)) %>% sample(),
                            TRT01AN = c("Drug","Placebo") %>% sample(size=n*12, replace=TRUE))
```

```{r echo = FALSE}
spaghetti_sim %>% head() %>%
  kableExtra::kable(align = 'c')
```

#### Basic Spaghetti plot
```{r, message=FALSE, warnings=FALSE, fig.dim = c(10, 7)}
p_spaghetti <- spaghetti_sim %>% 
  ggplot(aes(X, Y, group = SUBJIDN, colour = TRT01AN)) + 
  geom_point() + geom_line(size = 0.3) + theme_bw() + 
  labs(y="Y values", 
       x="Months since start of study treatment",
       colour = "Actual Treatment for Period 01 (N)") +
  theme(legend.background = element_rect(size=0.1, linetype="solid", 
                                         colour ="black"),
        legend.position="bottom", legend.box = "horizontal")
p_spaghetti
```

#### Spaghetti Plot with Broken Y
Different scales presented in the same plot when outliers are presented, to enlarge the detailed part of small values.

```{r, message=FALSE, warnings=FALSE, fig.dim = c(10, 7)}
#library(gg.gap)

p_spaghetti_break <- gg.gap(plot=p_spaghetti, tick_width=c(1,70),
         segments=c(15,25), rel_heights=c(8,0,1),
         ylim=c(0,235)) 
p_spaghetti_break
```

### Spider Plot
#### Packages and Sample Data
Create a sample data set to visualize

```{r, message = FALSE, warning = FALSE, error = FALSE}
# Packages
library(ggrepel)

# Data
sp <- data.frame(subjidn = rep(1:5, times = c(5,4,5,3,4)),
                 trtp = rep(c('drug','placebo'), times = c(8,13)),
                 avisit = c(0:4,0:3, 0:4, 0:2, 0:3),
                 aval = c(0,5,15,20,20,
                          0,-10,-20,-15,
                          0,-30,-25,-35,-30,
                          0,15,30,
                          0,-20,-15,-20))
```

```{r echo = F}
sp %>% 
  head(n=5) %>%
  kableExtra::kable(align = 'c')
```

#### Basic Spider Plot

```{r, message = FALSE, warning = FALSE, error = FALSE}
basic_spider <- ggplot(sp, aes(x = avisit, y = aval, group = subjidn)) +
  geom_line()

basic_spider
```

#### Adding Customizations

Add a few customizations to the spider plot

1. Line color is determined by `trtp` value
2. Add points to each line 
3. Add a dashed reference line at Y = 0
4. Specify custom colors, name the legend
5. Specify Y-axis goes from -40 to 40, by increments of 10
6. Add in a Y-axis label
7. Add in a X-axis label
8. Specify a base theme
9. Move legend to bottom of graph

#### Customized Spider Plot

```{r, message = FALSE, warning = FALSE, error = FALSE}
custom_spider <- ggplot(sp, aes(x = avisit, y = aval, group = subjidn, color = trtp)) +                             
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_manual("Planned Treatment Arm", values = c('#00bbff','#89d329')) +
  scale_y_continuous(limits = c(-40,40), breaks = seq(-40, 40, by = 10)) +      
  ylab("Change in Target Lesion from Baseline (%)\n") +                         
  xlab("Time (weeks)") +                                                        
  theme_light() +                                                               
  theme(legend.position = "bottom")                                             
  
custom_spider
```

#### Subject Labels Customization

Add subject Labels (IDs) at the end of each line

```{r}
sp_ends <- sp %>% 
  group_by(subjidn) %>% 
  top_n(1, avisit) 
```

```{r, echo = F}
sp_ends %>%
  kableExtra::kable(align = 'c')
```

```{r, warning = F, message = F}
# library(ggrepel)

custom_spider +
  geom_text_repel(
    aes(label = subjidn),
    color="black",
    data=sp_ends,
    size = 3,
    direction = "x",
    hjust = 1
  )
```

### Survival Plot 
#### Kaplan-Meier statistics and plotting

In the following example the _survfit_ function from the _survival_ package is used to calculate Kaplan-Meier statistics from time-to-event data. The model statistics can be inspected (using _broom_ - a generic function to extract statistics from R models). 

Passing the model to the _ggsurvplot_ function from the _survminer_ package creates a Kaplan-Meier curve. The configuration tries to mimic the known SAS output as close as possible (e.g. number at risk table style etc.).

#### Packages and Sample Data
```{r, message = FALSE, warning = FALSE, error = FALSE}
# Packages
library(survminer)
library(survival)
library(broom)
library(flextable)

# Data
adtte <- haven::read_xpt(
  paste0("https://github.com/phuse-org/TestDataFactory/",
         "raw/main/Updated/TDF_ADaM/adtte.xpt"))
``` 

Filter time-to-event parameter and select required variables. The piping command directly passed filtered and selected data to the `survfit` function and creates the model. 

>**Note:** The event parameter from survival function (survival::Surv) is the status   indicator, normally 0=alive, 1=death; while ADTTE.CNSR=0 usually means event  occurred(e.g., death), ADTTE.CNSR=1 represents censoring. Thus, “1-CNSR” is used here to  accommodate the CDISC ADaM standard.

```{r}
surv_model <- adtte %>%
  filter(PARAMCD == "TTDE") %>%
  select(STUDYID, USUBJID, PARAMCD, AVAL, CNSR, TRTA) %>%
  survfit(Surv(AVAL, 1-CNSR) ~ TRTA, data = .)
```

#### Inspecting fitted survival model

```{r, eval = F, echo = T}
head(tidy(surv_model))  
```

```{r, echo = F, eval = T}
head(tidy(surv_model)) %>%
 kableExtra::kable(align = 'c')
```
#### Plotting custom configured Kaplan-Meier curves without confidence intervals

>**Note:** Let´s assume a month is defined as 30.4375 (days); 
The xscale parameter d_m converts days (input) to month.
If six months breaks are required for the numbers-at-risk table this would mean: 
break.x.by = 182.625 (6*30.4375).

```{r, fig.width=15, fig.height=10, out.width="680px"}
ggsurvplot(
  fit = surv_model,
  data = adtte,
  risk.table = TRUE,
  #ylab = ylabs,
  xlab = "Months",
  linetype = "strata",
  conf.int = F,
  legend.title = "Randomized Treatment",
  legend = c(0.1, 0.1),
  #palette = c(color_trt1,color_trt2),
  risk.table.title = "Number of subjects at risk",
  risk.table.y.text = F,
  risk.table.height = .15,
  censor.shape = 1,
  censor.size = 3,
  ncensor.plot = F,
  #xlim = c(0,250),
  xscale = "d_m",
  break.x.by = 30.4375,
  break.y.by = .1,
  ggtheme = theme_survminer(
    font.main = c(10, "bold"),
    font.submain = c(10, "bold"),
    font.x = c(12, "bold"),
    font.y = c(12, "bold"),
  ) + theme(panel.border = element_rect(fill = NA)),
  tables.theme = theme_cleantable()
)
```

#### Plotting custom configured Kaplan-Meier curves with confidence intervals

```{r, fig.width=15, fig.height=10, out.width="680px"}
ggsurvplot(
  fit = surv_model,
  data = adtte,
  risk.table = TRUE,
  #ylab = ylabs,
  xlab = "Months",
  linetype = "strata",
  conf.int = T,
  legend.title = "Randomized Treatment",
  legend = c(0.1, 0.1),
  #palette = c(color_trt1,color_trt2),
  risk.table.title = "Number of subjects at risk",
  risk.table.y.text = F,
  risk.table.height = .15,
  censor.shape = 1,
  censor.size = 3,
  ncensor.plot = F,
  #xlim = c(0,250),
  xscale = "d_m",
  break.x.by = 30.4375,
  break.y.by = .1,
  ggtheme = theme_survminer(
    font.main = c(10, "bold"),
    font.submain = c(10, "bold"),
    font.x = c(12, "bold"),
    font.y = c(12, "bold"),
  ) + theme(panel.border = element_rect(fill = NA)),
  tables.theme = theme_cleantable()
)
```
