## Formatting

### Post Processing
By default, Tplyr will build your table and store it as a tibble. It can be accessed directly in your environment by simply calling it.

```{r}
head(my_table, n = 9)
```

Since it is tibble, you are free to further process or wrangle it to your liking. Below we'll apply some light formatting using a combination of `Tplyr` and `dplyr`:

1. Remove repeating variable labels and insert breaks between variable rows
2. Reorder the columns
3. Remove extraneous columns not of interest for display (i.e. meta data created by Tplyr) 

```{r, message = F, warning = F}
library(dplyr)

my_table <- my_table %>%
  
  # remove repeating labels
  apply_row_masks(., row_breaks = TRUE) %>%
  
  # specify order of relevant variables
  select(row_label1, 
         row_label2,
         `var1_Xanomeline High Dose`,
         `var1_Xanomeline Low Dose`,
         var1_Placebo,
         var1_Total)  
```

We can see the formatting has taken effect by recalling it in our environment. Specifically, compare the `row_label1` variable below to the previous section while also noting the order of columns has changed to our specification.

```{r}
head(my_table, n = 9)
```

### Displaying

While `Tplyr` aided us in *building* a summary tables, other packages exist to help us *display* them. One package we will focus on is the `flextable` package. This table display package is quite powerful and offers a high degree of customization.

We turn the interested reader to the <a href="https://ardata-fr.github.io/flextable-book/"> flextable book</a> to view additional examples.

```{r, warning = F, message = F}
library(flextable)

# a basic flextable
my_flextable <- my_table %>%
  
  # start flextable 
  flextable() %>%
  autofit()
```

```{r}
my_flextable
```

We can apply some `flextable` formatting to alter the display of the table.

```{r}
# a nicer flextable
my_flextable <- my_table %>%
  
  # start flextable 
  flextable() %>% 
  autofit() %>%
  
  # add some padding between rows
  padding(padding = 0.5) %>%
  
  # adjust width of first two columns
  width(j = 1:2, width = 4) %>%
  
  # align treatment columns to center
  align(part = "all", align = "center", j = 3:6) %>%
  
  # column header labels
  set_header_labels(., values = list(
    row_label1 = 'Variable',
    row_label2 = ' ',
    `var1_Xanomeline High Dose` = 'Xanomeline \nHigh Dose',
    `var1_Xanomeline Low Dose` = 'Xanomeline \nLow Dose',
    var1_Placebo = 'Placebo',
    var1_Total = 'Total')) %>%
  
  # header + footers
  add_header_lines(values = "Table: Demographics (Safety Analysis Set)") %>%
  add_footer_lines(values = "This was produced in R!") %>%
  
  # font size, font name
  fontsize(part = "all", size = 8)
  # font()
  # font(part = "all", fontname = "Times")  
  # This errors, perhaps version issue.  -- SZ
```

```{r echo = F}
my_flextable
```

## Exporting

To export our table to MS Word (.docx), we may use the `officer` package. This package simplifies working with various Microsoft Office formats and integrates nicely with `flextable`.

```{r, warning = F, message = F, eval = F}
library(officer)

# send the flextable to .docx output
read_docx() %>%
  body_add_flextable(my_flextable) %>%
  print(target = "my_document.docx")
```

In your working directory, you should now see the file `my_document.docx` has been created and contains your table.

