# Figures & Plots

In this section, basic useage of the `ggplot2` package is covered. Common clinical trial displays are then created and customized in a step wise manner.
## Basics

### Building a plot using ggplot2

#### Packages and Sample Data
```{r, echo = TRUE, message = FALSE, warning = FALSE}
# Packages
library(haven)
library(ggplot2)

# Data
adam_path <- "https://github.com/phuse-org/TestDataFactory/raw/main/Updated/TDF_ADaM/"
adsl <- as.data.frame(haven::read_xpt(paste0(adam_path, "adsl.xpt")))
```

Let's create a basic scatter plot of weight vs height.
```{r, eval = F}
# basic scatter plot of weight vs height
my_scatter_plot <- ggplot(adsl, aes(x = HEIGHTBL, y = WEIGHTBL)) +
  geom_point()
my_scatter_plot
```


### Exporting plots
You may export plots as png files a few ways. If your plot is created in ggplot2, you can use the `ggsave()` function to export as png:
```{r, eval = F}
# save plot as a png file
ggsave(plot = my_scatter_plot, 
       filename = "my_plot_output_1.png", 
       width = 7, 
       height = 5, 
       units = "in")
```

The more general way to save plots as png files is to use the `png()` function. It can work with ggplot2, but also plots created in base R.
```{r, eval = F}
png(filename = "my_plot_output_2.png", 
    width = 7, 
    height = 5, 
    units = "in", 
    res = 300)

print(my_scatter_plot)
dev.off()
```






