### Waterfall Plot
#### Packages and Sample Data

```{r, message = FALSE, warning = FALSE, error = FALSE}
# Packages
library(gridExtra)
library(grid)

# Data
wp <- data.frame(subjidn = 1:30,
                 trtp = sample(c('Drug','Placebo'), replace = T, 30),
                 aval = runif(30, min = -40, max = 40))
```

```{r echo = F}
head(wp) %>% 
  kableExtra::kable(align = 'c')
```

#### Basic Waterfall Plot
Create an initial waterfall plot

```{r, message = FALSE, warning = FALSE, error = FALSE}
basic_waterfall <- ggplot(wp, aes(y = aval,x = reorder(subjidn, -aval))) +
  geom_bar(stat = "identity")

basic_waterfall
```


#### Adding Customizations
Add a few customizations to the waterfall plot

1. Bar fill color is determined by trtp value
2. Specify custom colors, name the legend
3. Specify Y-axis goes from -40 to 40, by increments of 10
4. Add in a Y-axis label
5. Specify a base theme
6. Remove the X-axis
7. Move legend to bottom of graph

#### Customized Waterfall Plot

```{r, message = FALSE, warning = FALSE, error = FALSE}
custom_waterfall <- ggplot(wp, aes(y = aval, x = reorder(subjidn, -aval), fill = trtp)) +                            
  geom_bar(stat = "identity") +
  scale_fill_manual("Planned Treatment Arm", values = c('#00bbff','#89d329')) +
  scale_y_continuous(limits = c(-40,40), breaks = seq(-40, 40, by = 10)) +      
  ylab("Maximum reduction of tumor size (%)\n") +                              
  theme_light() +                                                               
  theme(axis.title.x = element_blank(),                                         
        axis.line.x  = element_blank(),
        axis.text.x  = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "bottom")                                             
          
custom_waterfall
```

#### Study Example

* A special waterfall plot layout is needed in a real study. In this layout, biomarker information in the subject level needs to be added at the bottom of the waterfall plots.

* The dataset for the plot was derived from ADRS and ADSL in SAS; simulated data is used in this demo.

Simulate Data:
```{r,  message=FALSE, warnings=FALSE}
set.seed(100)  

n <- 120   # size/records of simulated data

dat_all <- 
  data.frame(SUBJID = 120010100:(120010100+n-1),
           AVAL = c(rnorm(round(0.8*n), 0, 20), rep(0, round(0.2*n))) %>% sample(),
           OVERALLRESP = c("PR", "SD","PD") %>% sample(size=n, replace=TRUE),
           AMEDGRPN = seq(10, 50, 10) %>% sample(size=n, replace=TRUE),
           DOR = rpois(n, 40),
           AVISIT = c("C1", "C2", "C3","EOT") %>% sample(size=n, replace=TRUE),
           ATMLOSS_L = c("E", "L", "Data unavailable") %>% sample(size=n, replace=TRUE),
           ATMLOSS_P = c("E", "L", "Data unavailable") %>% sample(size=n, replace=TRUE),
           ATMLOSS_R = c("E", "L", "Data unavailable") %>% sample(size=n, replace=TRUE),
           IDFOOT = "Bayer: /study/path/.../f_waterfall.sas               30NOV2021 16:06"
           ) %>%
  mutate_at(vars("OVERALLRESP", "DOR", "IDFOOT"), as.character)
```

* X: SUBJID 
* Y: AVAL (derived from ADRS.AVAL when ADRS.PARAM = "Maximum Tumor Reduction (%)") 
* Label: OVERALLRESP (derived from ADRS.AVAL when ADRS.PARAM = "Best Overall Response") 
* Subset: AMEDGRPN (5 groups)
* A graph function is created in the real study for different analysis groups, in this demo, we subset data to AMEDGRPN = 50. 

```{r, echo=FALSE, message=FALSE, warnings=FALSE}
dat_all %>% 
  filter(AMEDGRPN==50) %>% 
  select(SUBJID, AVAL, OVERALLRESP, AMEDGRPN, 
         DOR, AVISIT, ATMLOSS_L, ATMLOSS_P, ATMLOSS_R) %>%
  head() %>%
  kableExtra::kable(align = 'c')

dat <- dat_all %>% filter(AMEDGRPN==50)
```

**Create a waterfall plot with simulated data and below customization**

1. Add x/y-axis labels through function "labs"
2. SUBJID has long digits, below functions are used to avoid overlapping at x-axis:
    + function stringr::str_wrap: add split character “\n" between digits
    + function gsub: add space between digits to enable the use of str_wrap
    + function stringr::str_replace_all: remove space
3. Specify legend title, order/colors (similar to SAS sgplot - dattrmap)
4. Annotation on the top of the bar when Y=0  
5. Adjust background, legend, and size/color/font of x/y-axis aesthetics through Theme

```{r, message=FALSE, warnings=FALSE, fig.dim = c(9, 4)}
waterfall.plot <- dat %>% ggplot(aes(reorder(SUBJID, -AVAL), AVAL, fill =OVERALLRESP)) + 
    geom_bar(stat="identity") +
  labs(x = "Subject", 
       y = "Best % Change from baseline \n in sum of diameters \n (target lesions)\n") +
  scale_x_discrete(labels = function(x) stringr::str_wrap(gsub("([0-9])([0-9])", "\\1 \\2 ", x), 
                                                     width = 5) %>% 
                     stringr::str_replace_all(" ", "")) +
  scale_fill_manual("Best Response",
                    breaks = c("PR", "SD","PD"),
                    values=c("PR"='#89d329',
                             "SD"="#756bb1",
                             "PD"='#00bbff')) + 
  geom_text(aes(label = if_else(AVAL == 0,OVERALLRESP,""),fontface="bold"), 
            vjust = -1,
            size=3,
            color="black") + theme_bw() +     
  theme(
    axis.text = element_text(size=12,color="black",face = "bold"),  
    axis.title.y = element_text(size=12, face="bold"), 
    axis.title.x = element_blank(),  
    legend.background = element_rect(color = "steelblue", linetype = "solid"),
    legend.justification = c(1, 1), 
    legend.position = c(1, 1),
    legend.direction = "horizontal",
    legend.text = element_text(size=8, color = "black", face = "bold"),
    legend.title = element_text(size=8, color = "black", face = "bold"),  
    plot.caption = element_text(hjust = 0, size = 10, color = "blue"), 
    plot.caption.position =  "plot"
  ) 

waterfall.plot
```

As requested from the study, more information at subject level needs to be added in the bottom of the waterfall plots. Thus, two more plots are created (add-in plot1/2) to display the subject level information. 

* Add-in plot 1: visit and duration of response information at subject level
```{r, message=FALSE, warnings=FALSE, fig.dim = c(9, 3)}
var <- c("DOR", "AVISIT")
var_label <- c("Duration (days)", "Timepoint")

add.plot1 <- dat %>%
  reshape2::melt(measure.vars = eval(var), value.name = "label", variable.name = "layer") %>%
  mutate(layer = factor(layer, levels = var, labels = var_label)) %>%
  ggplot(aes(reorder(SUBJID, -AVAL))) +
  geom_text(aes(y = layer, label = label), size = 3, fontface = "bold") +
  labs(y = "", x = NULL) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(
      size = 10,
      colour = "black",
      face = "bold"
    ),
    axis.line = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_blank(),
    panel.grid = element_blank(),
    strip.text = element_blank()
  ) +
  coord_fixed(ratio = .8)
add.plot1
```

* Add-in plot 2: biomarker-related information at subject level, footnotes are added in this plot
  + wrap long footnote by adding "\\n\" or using stringr::str_wrap
  + display SAS macro variable "&idfoot."

Footnotes:
```{r}
footnote1 <- 'Footnote1: "\\n\" can be used to split long footnote into next line.'
footnote2 <- "Footnote2: To avoid manually adding split character. The function stringr::str_wrap	can be used here to wrap the long text with a specified width."
footnote <- lapply(c(footnote1,
                     footnote2,
                     "",
                     dat$IDFOOT[1]),
                   function(x) stringr::str_wrap(x, width=120)) %>% # apply str_wrap to individual footnote
  unlist() %>%       # convert list structure to vector
  stringr::str_flatten('\n')  # add split character(new line) between footnotes
```

```{r, error = FALSE, message=FALSE, warnings=FALSE, fig.dim = c(9, 3)}
var <- c("ATMLOSS_L", "ATMLOSS_P","ATMLOSS_R")
var_label <- c("Local", "Prospective", "Retrospective")

add.plot2 <- dat %>%  
  reshape2::melt(measure.vars = eval(var), 
                 value.name = "label",
                 variable.name = "layer") %>%
  mutate(label=case_when(
    label == "L" ~ "ATM Loss",
    label == "E" ~ "ATM Expressed",      
    label == "9" ~ "Data unavailable",
    TRUE ~ label
  )) %>% 
  mutate(layer = factor(layer, levels = rev(var), labels = rev(var_label))) %>% 
  ggplot() +
  aes(reorder(SUBJID, -AVAL), layer, color=label,shape=label) +
  geom_point(size=3)+
  scale_shape_manual(breaks = c("ATM Loss","ATM Expressed", "Data unavailable"), 
                     values = c("ATM Loss"=15,"ATM Expressed"=0, 
                                "Data unavailable"=7))+
  scale_color_manual(values = c("ATM Loss"="black", "ATM Expressed"="black", 
                                "Data unavailable"= 'black'))+
  theme_classic()+
  theme(axis.text=element_text(size=10, colour = "black",face = "bold"),
        axis.title=element_blank(),
        axis.line = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=10, color = "black", face = "bold"),
        legend.position = "bottom",
        panel.border = element_blank(),
        panel.grid = element_blank(), 
        strip.text = element_blank(),
        plot.caption = element_text(hjust = 0, size = 10), 
        plot.caption.position =  "plot"
  )+
  coord_fixed(ratio=.9)+ 
  labs(caption = footnote)
add.plot2
```

* The following functions are used to combine three plots aligned with x value.
  + ggplot2::ggplotGrob
  + gridExtra::gtable_rbind
  + grid::grid.draw
  
* Align the three plots with the same x-axis (SUBJID). 
  + waterfall.plot 
  + add.plot1 
  + add.plot2 
  
```{r, message=FALSE, warnings=FALSE, fig.dim = c(10, 7)}
p1 <- waterfall.plot %>% ggplotGrob()
p2 <- add.plot1 %>% ggplotGrob()
p3 <- add.plot2 %>% ggplotGrob()
gtable_rbind(p1, p2, p3,
             size='first') %>% grid.draw()
```