### Spider Plot
#### Packages and Sample Data
Create a sample data set to visualize

```{r, message = FALSE, warning = FALSE, error = FALSE}
# Packages
library(ggrepel)

# Data
sp <- data.frame(subjidn = rep(1:5, times = c(5,4,5,3,4)),
                 trtp = rep(c('drug','placebo'), times = c(8,13)),
                 avisit = c(0:4,0:3, 0:4, 0:2, 0:3),
                 aval = c(0,5,15,20,20,
                          0,-10,-20,-15,
                          0,-30,-25,-35,-30,
                          0,15,30,
                          0,-20,-15,-20))
```

```{r echo = F}
sp %>% 
  head(n=5) %>%
  kableExtra::kable(align = 'c')
```

#### Basic Spider Plot

```{r, message = FALSE, warning = FALSE, error = FALSE}
basic_spider <- ggplot(sp, aes(x = avisit, y = aval, group = subjidn)) +
  geom_line()

basic_spider
```

#### Adding Customizations

Add a few customizations to the spider plot

1. Line color is determined by `trtp` value
2. Add points to each line 
3. Add a dashed reference line at Y = 0
4. Specify custom colors, name the legend
5. Specify Y-axis goes from -40 to 40, by increments of 10
6. Add in a Y-axis label
7. Add in a X-axis label
8. Specify a base theme
9. Move legend to bottom of graph

#### Customized Spider Plot

```{r, message = FALSE, warning = FALSE, error = FALSE}
custom_spider <- ggplot(sp, aes(x = avisit, y = aval, group = subjidn, color = trtp)) +                             
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_manual("Planned Treatment Arm", values = c('#00bbff','#89d329')) +
  scale_y_continuous(limits = c(-40,40), breaks = seq(-40, 40, by = 10)) +      
  ylab("Change in Target Lesion from Baseline (%)\n") +                         
  xlab("Time (weeks)") +                                                        
  theme_light() +                                                               
  theme(legend.position = "bottom")                                             
  
custom_spider
```

#### Subject Labels Customization

Add subject Labels (IDs) at the end of each line

```{r}
sp_ends <- sp %>% 
  group_by(subjidn) %>% 
  top_n(1, avisit) 
```

```{r, echo = F}
sp_ends %>%
  kableExtra::kable(align = 'c')
```

```{r, warning = F, message = F}
# library(ggrepel)

custom_spider +
  geom_text_repel(
    aes(label = subjidn),
    color="black",
    data=sp_ends,
    size = 3,
    direction = "x",
    hjust = 1
  )
```
